 Casting multiple shadows: high-dimensional interactive data visualisation with tours and embeddings

### 2020-04-17 paper.Rmd
update section

$$
\text{perplexity}_i = \exp(-\log(2) \sum_{i \ne j}p_{j|i}\log_2(p_{j|i}))
$$
As the perplexity increases, $sigma_^2_{i}$ increases, until its bounded
above by the number of observations , $n-1$, in the data, corresponding to  
$\sigma^2_{i} \rightarrow \infty$. This essentially turns $t-SNE$ into a 
nearest neighbours algorithm, $p_{i|j}$ will be close to zero for all 
observations that are not in the $\mathcal{O}(\text{perplexity}_i)$
neighbourhood graph of the $i$th observation [@Van_Der_Maaten2014-zn].

>>>>

$$
\text{perplexity}_i = \exp(-\log(2) \sum_{i \ne j}p_{j|i}\log_2(p_{j|i}))
$$
As the perplexity increases, $\sigma^2_{i}$ increases, until its bounded
above by the number of observations , $n-1$, in the data, corresponding to  
$\sigma^2_{i} \rightarrow \infty$. This essentially turns $t-SNE$ into a 
nearest neighbours algorithm, $p_{i|j}$ will be close to zero for all 
observations that are not in the $\mathcal{O}(\text{perplexity}_i)$
neighbourhood graph of the $i$th observation [@Van_Der_Maaten2014-zn].
